% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}
    \project{PELI ComPASS}{August 2014 - Current}
    {\website{https://preferencebasedliving.com/}{Preference Based Living}}
    {Preference Based Living is a collaboration of multiple universities that aims to improve the use of prefences in healthcare. PELI ComPASS is a web application designed for practitioners to use while interviewing patients to collect their preferences.  Practitioners can then use the application to track satisfaction among preferences and generate data-driven reports.}
    {web design, agile, data collection, data visualization, ruby on rails, drupal}

	\project
	{vizSlice}{August 2015 - May 2017}
	{\website{http://vizslice.csi.miamioh.edu}{vizSlice} \gitlab{rakJennings/vizSlice} }
	{
	    Visualizes program slicing data generated from srcSlice.  Programs are visualized utilizing D3 for interactive treemaps, bipartite graphs, and parallel coordinates plots.  Data is generated via srcSlice and then parsed and formatted for use in visualizations.
	}
	{data visualization, program slicing, D3}
	 
	\project
	{Concentration Game for the Analysis of Preschool Learning}{Mar. 2013 - Dec. 2015}
	{Undergraduate Research}
	{
	    Developed a responsive web application for Psychology Department.  The application was utilized for the collection of data during the play of a concentration game on an IPad.
	}
	{web design, game design, data collection}
				
\end{projects}